Variability of Planetary Mass Companion 2M1207 B

### 2015-08-17 summary/letter/letter_v1.tex
edited several parts of the letter

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\begin{document}
\title{Variability of Planetary Mass Companion 2M1207 B}
\shorttitle{Variability of 2M1207 B}
\author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
\affil{University of Arizona}

@@

\section{Observation}
We took high contrast direct imaging observation of 2M1207
system on UT 2014 April 11 using HST.
(\textit{HST} Proposal GO-13418, PI: D. Apai). The data were acquired
with the Wide Field Camera 3 (WFC3) in filter F125W
and F160W using the $256\times256$ sub-array mode. We observed
2M1207 system in continuous 6 HST orbits and obtained a data-set that
have a temporal resolution of $\sim1.5$ minutes and baseline of $\sim
8$ hours.

The observation was initially designed to apply standard roll
subtraction to remove the primary star. The telescope roll angles for
data taken in orbit 1, 3, 5 and those taken in orbit 2, 4, 6 have a
difference of $25^{\circ}$, thus the companion would appear at
different position relative to the primary 
and the primary in the two data set can be subtracted from each other.
In each orbit we took a sequence of 13 SPARS25 exposures with
NSAMP=10, alternating between F160W and F125W filters, with 2-3
identical exposures in one exposure sequence. To improve PSF
sampling and reduce the risk caused by bad pixels, we applied standard 4
point dithering. In each orbit, exposures were taken with dithering
position 1 -- 4 sequently. To sum, we obtained 70 multi-acuum images
for filter F125W and 64 images for filter F160W with exposure time of
88.4 seconds for both two filters.

>>>>

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\begin{document}
\title{Variability of Planetary Mass Companion 2M1207 B}
\shorttitle{Variability of 2M1207 B}
\author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
\affil{The University of Arizona}

@@

\section{Observation}
We took high contrast direct imaging observation of 2M1207 system on
UT 2014 April 11 using HST.  (\textit{HST} Proposal GO-13418, PI:
D. Apai). The data were acquired with the Wide Field Camera 3 (WFC3)
in filter F125W ($\lambda_{\mbox{pivot}}$ = 1245.9 nm. FWHM = 301.5
nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM = 287.9 nm)
using the $256\times256$ sub-array mode. We observed 2M1207 system in
six contiguous HST orbits and obtained a data-set that have a temporal
resolution of $\sim1.5$ minutes and baseline of 8 hours and 40
minutes, interrupted by Earth occultaions of 58 minutes every  94 minutes.

The observations was initially designed to apply two-roll
PSF-subtraction (e.g. \cite{Song2006}) to remove the background light from the primary star. The
telescope roll angles for data taken in orbit 1, 3, 5 and those taken
in orbit 2, 4, 6 differed by $25^{\circ}$, thus the roll displacement
of the companion is 0.34 .  In
each orbit we took a sequence of 13 SPARS25 exposures with NSAMP=10,
alternating between F160W and F125W filters, with 2-3 identical
exposures in one exposure sequence. To improve PSF sampling and reduce
the risk caused by bad pixels, we applied standard 4 point
dithering. In each orbit, exposures were taken with dithering position
1 -- 4 sequently. To sum, we obtained 70 multi-acuum images for filter
F125W and 64 images for filter F160W with exposure time of 88.4
seconds for both two filters.
